The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population

### 2017-03-18 repeater-vladata.tex
restructured table. spectrum discussion ok

\subsection{Multi-Observatory Burst Spectrum}
Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA, while two were observed simultaneously with all four observatories (Figure \ref{fig:multi}). Of these bursts, only one VLA burst (on MJD 57648) was simultaneously detected by another observatory (Arecibo). The VLA and Arecibo burst detections had significances of 25$\sigma$\ and 39$\sigma$ with integrated flux densities of 111 mJy and 14 mJy, respectively.

Figure \ref{fig:sgram} shows a dynamic spectrum for the 57648 burst with the VLA and AO data aligned in time. The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the same temporal grid after correcting for barycentric and dispersion measure offsets. The dispersion correction for both data sets assumed a DM of 560.5 pc cm$^{-3}$, which was typical of the source during the observing campaign \citep{WEIRD}. The regridded dynamic spectrum has an apparent DM error that is evident both as a frequency-dependent time drift within the Arecibo observation and as an offset between the Arecibo and VLA bursts. Both of these drifts are consistent with an effective DM (i.e., one that maximizes the detection S/N ratio) of $sim$565 pc cm$^{-3}$. This is consistent with modeling of the VLA spectrum described in \S \ref{sec:spec}.

Three of the four VLA bursts with simultaneous observing coverage by Arecibo were not detected at Arecibo. Even the one simultaneous detection at Arecibo was an order of magnitude fainter than seen by the VLA, so it is clear that the 3~GHz burst flux is not correlated with that at 1.4~GHz.

@@

\begin{table*}
\caption{Properties of Bursts from \frb}
\centering
\begin{tabular}{lccccccccc}
\hline
Date                & Image S/N & S$_{\rm{I,int}}$	& S$_{\rm{V}}$ 	& E$_{\rm{int}}$ & DM$_{\rm{opt}}$ & dt 	 & S$_{\rm{I,peak}}$ & Center & FWHM \\
(MJD)               &           & (mJy) 			& (mJy) 		& ($10^{38}$\ erg)& (pc cm$^{-3})$ & (ms) & (mJy) 	& (GHz)  & (MHz) \\ \hline
57623.74402686      & 38 		& 194				& +3			& 11 			& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 \\
57633.67986367      & 179 		& 1500				& --35 			& 98				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 	& 3.2 		& 510 \\
57633.69515938\tablenotemark{a} & 15 & 69			& +2			& 7  			& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& 290 \\
57638.49937435      & 12 		& 55				& +5 			& 3  			& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 \\
57643.45730263      & 100 		& 508				& --5 			& 34 			& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 	& 2.8 		& 510 \\
57645.42958602      & 13 		& 64 				& +3			& 4  			& 563$^{+5}_{-4}$ 	& 1.0$\pm0.7$		 	& 170 		& 2.8 		& 380 \\
57646.46600650\tablenotemark{a} & 20 & 87			& +1			& 10 			& 569$\pm5$ 		& 2.7$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& 430 \\
57648.43691490\tablenotemark{b} & 25 & 111			& +9			& 7  			& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 \\
57649.45175697      & 36 		& 167				& +1			& 12 			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 \\ \hline
\end{tabular}
\tablenotetext{a}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
\tablenotetext{b}{Detected simultaneously with Arecibo between 1.15 and 1.73~GHz.}
\label{tab:spec}
\end{table*}

@@

\section{discussion}
\label{sec:disc}
\subsection{Burst Spectra}
We present the first simultaneous detection of an FRB with multiple telescopes and over frequencies from 1.2 to 3.5~GHz. After correcting for barycentric and dispersion delays, we find a residual temporal drift in the burst spectrum. This is consistent with \citet{WEIRD}, which uses bright, coherently-dedispersed bursts to define a heuristic that distinguishes between intrinsic and extrinsic dispersion-like effects. The low-resolution dynamic spectra presented here cannot distinguish between these two effects. However, by assuming that the extrinsic (true) DM is consistent with the long-term average of 560.5 pc cm$^{-3}$, we can ascribe the observed burst drift (Figure \ref{fig:sgram}) to intrinsic effects. Under this assumption, the burst drift is intrinsic and consistent with the intrinsic drft rate measured in \citet[$\sim$100~MHz/ms;][]{WEIRD}.

The 57648 burst is nearly an order of magnitude brighter near 3~GHz than at 1.4~GHz. Expressed as a spectral index ($S_{\nu} \propto \nu^{\alpha}$), we find $\alpha\approx2.7$. However, the bursts detected here and described in \citet{WEIRD} make it clear that burst spectral power is not well described by a powerlaw.

Given the high sensitivity of Arecibo...
Even the one AO detection is 10x fainter...
** is one of three VLA bursts with L-band coverage by Arecibo, which implies that those bursts had a smaller spectral width. However, all three VLA bursts with L-band Arecibo observations were relatively weak, so it is difficult to rule out L-band emission entirely. However, as described in \S \ref{sec:spec}, some of the VLA bursts peak within the band from 2.5 to 3.5~GHz, which implies a much smaller spectral coverage for typical bursts.

Propagation effects (e.g., scintillation, scattering) can also modify the radio signal in a variety of ways and the duration of the emission in the source frame is not known \citep{2016arXiv160505890C}. \citet{CORDES} describe a model where plasma lensing near the source of an FRB can magnify radio emission by orders of mangitude. That model argues that the simultaneous appearance of a burst from 1.2 to 3.5~GHz requires a lens with the focal frequency be $\gtrsim 3.5$~GHz. This gives a constraint on the combination 
$$\frac{\rm DM_0}{a_{\rm AU}^2} \frac{d_{sl}d_{lo}/d_{so}}{1\, \rm kpc} \gtrsim (3.5 / 39.1)^2$$
where $DM_0$, $a$, and $d_*$\ are the electron column density of the lens, size of the lens, and lensing distances, respectively. A lens placed at $d_{sl}\approx1$~kpc is consistent with typical properties of the interstellar medium. Lenses that are influenced by the source would be much nearer to the source $d_{\sl} \ll 1$~kpc, requiring large values of $\frac{\rm DM_0}{a_{\rm AU}^2}$.

@@

-- Self-organized criticality in the sun. energy powerlaw=-1.7 \citep{2011SoPh..274...99A}
-- **Similarity to magnetar energy distribution**

The Lorimer burst was surprising for its unusually large flux with a lack of lower-significance detections. As more FRBs have been detected, we continue to be surprised by their apparent brightness of FRBs \citep{2016arXiv161105758R}. This perception has been validated with analysis of the FRB cumulative fluence distribution, which when modeled as a powerlaw ($dN/dF \propto F^{\alpha}$) has an index $-0.5<\alpha<-0.9$\ \citep{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}. For a uniform distribution of sources with a single luminosity, this index should be --1.5 \citep[the ``Euclidean'' distribution, e.g.,][]{2016MNRAS.462..941L}.

The energy distribution of \frb\ bursts has also produced some surprises. The nine bursts were detected with a wide range of significance (12 to 179$\sigma$) and the apparent burst energy distribution can be characterized as a powerlaw $dN/dE\propto E^{-1.6}$. If all FRBs luminosities are drawn from such a distribution, then their flux distribution will be determined by the underlying energy distribution and its interplay with redshift space distortions.

@@

>>>>

\subsection{Multi-Observatory Burst Spectrum}
Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA, while two were observed simultaneously with all four observatories (Figure \ref{fig:multi}). Of these bursts, only one VLA burst (on MJD 57648) was simultaneously detected by another observatory (Arecibo). The VLA and Arecibo burst detections had significances of 25$\sigma$\ and 39$\sigma$ with integrated flux densities of 111 mJy and 14 mJy, respectively. Assuming a powerlaw flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha\approx2.7$.

Figure \ref{fig:sgram} shows a dynamic spectrum for the 57648 burst with the VLA and AO data aligned in time. The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the same temporal grid after correcting for barycentric and dispersion measure offsets. The dispersion correction for both data sets assumed a DM of 560.5 pc cm$^{-3}$, which was typical of the source during the observing campaign \citep{WEIRD}. The regridded dynamic spectrum has an apparent DM error that is evident both as a frequency-dependent time drift within the Arecibo observation and as an offset between the Arecibo and VLA bursts. Both of these drifts are consistent with an apparent DM of $sim$565 pc cm$^{-3}$. This is consistent with modeling of the VLA spectrum described in \S \ref{sec:spec}.

Three of the four VLA bursts with simultaneous observing coverage by Arecibo were not detected at Arecibo. Numerous bursts were also detected by Arecibo during VLA observing, but were not detected by the VLA at 3~GHz. Considering this, and the order of magnitude difference in flux density for the one simultaneous burst detection, we conclude that the 3~GHz burst flux is not correlated with that at 1.4~GHz.

@@

\begin{table*}
\caption{Properties of Bursts from \frb}
\centering
\begin{tabular}{l|ccc|cccccc}
\hline
Date                & Image S/N & S$_{\rm{I,int}}$	& S$_{\rm{V}}$ 	& DM$_{\rm{opt}}$ 	& dt 			& S$_{\rm{I,peak}}$ & Center & FWHM & E$_{\rm{int}}$ \\
(MJD)               &           & (mJy) 			& (mJy) 		& (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
57623.74402686      & 38 		& 194				& +3			& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 11 			\\
57633.67986367      & 179 		& 1500				& --35 			& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 98				\\
57633.69515938\tablenotemark{a} & 15 & 69			& +2			& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& 290 & 7  			\\
57638.49937435      & 12 		& 55				& +5 			& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 3  			\\
57643.45730263      & 100 		& 508				& --5 			& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 34 			\\
57645.42958602      & 13 		& 64 				& +3			& 563$^{+5}_{-4}$ 	& 1.0$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
57646.46600650\tablenotemark{a} & 20 & 87			& +1			& 569$\pm5$ 		& 2.7$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& 430 & 10 			\\
57648.43691490\tablenotemark{b} & 25 & 111			& +9			& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
57649.45175697      & 36 		& 167				& +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 12 			\\ \hline
\end{tabular}
\tablenotetext{a}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
\tablenotetext{b}{Detected simultaneously with Arecibo between 1.15 and 1.73~GHz.}
\label{tab:spec}
\end{table*}

@@

\section{discussion}
\label{sec:disc}
\subsection{Burst Spectra}
We present the first simultaneous detection of an FRB with multiple telescopes and over frequencies from 1.2 to 3.5~GHz. At the same time, three other bursts had similar observing coverage but were not detected simultaneously. Given that the Arecibo detection is an order of magntude weaker than the VLA detection and that multiple VLA bursts appear largely within the 3~GHz band, we conclude that \frb\ burst spectra are not well described by a powerlaw. Instead, bursts spectrally are well-described by a Gaussian-like shape with a 500~MHz-scale envelope. This is consistent with \citet{WEIRD}, which uses high-resolution Arecibo spectra to identify rich spectral structure ("sub-bursts") intrinsic to each burst.

After correcting for barycentric and typical dispersion delays, the VLA/Arecibo burst spectrum shows a residual temporal drift. This drift can be interpreted as an excess DM of roughly 5 pc cm$^{-3}$. This excess DM is similar in size to the burst-to-burst variation in DM measured for the whole sample of VLA 3~GHz bursts and had been noted in earlier 1.4~GHz Arecibo observations of \frb \citep{2016arXiv160308880S}. The VLA bursts demonstrate that this ''excess'', burst-specific DM is seen up to 3~GHz. The simultaneous VLA/Arecibo burst shows that the (instantaneous) burst properties from 1.2 to 3.5~GHz are consistent with a single excess.

These features are generally consistent with intrinsic burst properties described in \citet{WEIRD}. That work uses bright, coherently-dedispersed bursts to define a heuristic that distinguishes between burst-specific and time-stationary dispersion-like effects. They show that the bursts are composed of "sub-bursts" that preferentially drift to lower frequencies at later times, which systematically biases DM measurements that maximize S/N ratio. Interestingly, our MCMC modeling of the VLA bursts shows a weak correlation between larger apparent DM and pulse width. This could be a signature of blending of many unresovled sub-bursts in a single VLA burst spectrum. Assuming a long-term average DM of 560.5 pc cm$^{-3}$, we can ascribe the observed excess DM to an intrinsic burst drift rate measured on the order of $\sim100$~MHz/ms.

The burst-specific DM structure could be intrinsic to the emission mechanism or induced during propagation. Radio waves can be modified in a variety of ways (e.g., scintillation, scattering) and the duration of the emission in the source frame is not known \citep{2016arXiv160505890C}. \citet{CORDES} describe a model where plasma lensing near the source of an FRB can magnify radio emission by orders of mangitude. That model argues that the simultaneous appearance of a burst from 1.2 to 3.5~GHz requires a lens with the focal frequency be $\gtrsim 3.5$~GHz. This gives a constraint on the combination 
$$\frac{\rm DM_0}{a_{\rm AU}^2} \frac{d_{sl}d_{lo}/d_{so}}{1\, \rm kpc} \gtrsim (3.5 / 39.1)^2$$
where $DM_0$, $a$, and $d_*$\ are the electron column density of the lens, size of the lens, and lensing distances, respectively. A lens placed at $d_{sl}\approx1$~kpc is consistent with typical properties of the interstellar medium. Lenses that are influenced by the source would be much nearer to the source $d_{\sl} \ll 1$~kpc, requiring large values of $\frac{\rm DM_0}{a_{\rm AU}^2}$.

@@

The nine bursts were detected with a wide range of significance (12 to 179$\sigma$) and the apparent burst energy distribution can be characterized as a powerlaw $dN/dE\propto E^{-1.6}$. With only 9 VLA bursts, it is difficult to draw strong inferences, but a similar energy index has been observed in X-ray fluxes of solar flares \citep{2011SoPh..274...99A} and gamma-ray fluence for soft-gamma repeaters \citep{2000ApJ...532L.121G, 2011ApJ...739...94S}. This distribution is similar to that seen in earthquakes and other phenomena generally termed ''self-organized criticality'' \citep{2011SoPh..274...99A}.

FRB detections have often been far brighter than the limiting brightness of telescopes detecting them \citep{2007Sci...318..777L, 2016arXiv161105758R}. This perception has been supported by analysis that suggests that the cumulative flux distribution ($dN/dF \propto F^{\alpha}$) is relatively flat \citep[$-0.5<\alpha<-0.9$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}. For a uniform distribution of sources, we expect a ''Euclidean distribution'' with $\alpha=-1.5$ \citep{2016MNRAS.462..941L}.
V/Vmax
If all FRBs luminosities are drawn from such a distribution, then their flux distribution will be determined by the underlying energy distribution and its interplay with redshift space distortions.

@@

Studying a cosmological source population will require making redshift corrections. The limited envelope of bursts from \frb\ suggest that spectral extrapolations based on a spectral index are not likely to be reliable. It is more reasonable to treat the FRB rate as a frequency-dependent property, than to scaling from a single rate via a spectral index.
